### 2024-05-22 getting-started.qmd
20240522 - fix error
20240522 - fix cross-reference
20240522 - weekly calculations

We already load players' week-by-week statistics [above](#downloadActualStats).
Nevertheless, we could compute players' weekly statistics from the play-by-play data using the following syntax:

@@

nfl_actualStats_weekly <- nflfastR::calculate_player_stats(
  nfl_pbp,
  weekly = TRUE)
```

>>>>

We already load players' week-by-week statistics [above](#sec-downloadActualStats).
Nevertheless, we could compute players' weekly statistics from the play-by-play data using the following syntax:

@@

nfl_actualStats_offense_weekly <- nflfastR::calculate_player_stats(
  nfl_pbp,
  weekly = TRUE)

nfl_actualStats_defense_weekly <- nflfastR::calculate_player_stats_def(
  nfl_pbp,
  weekly = TRUE)

nfl_actualStats_kicking_weekly <- nflfastR::calculate_player_stats_kicking(
  nfl_pbp,
  weekly = TRUE)
```
